Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-01-21 paper.tex
Mostly proved the double dagger thing

@@

  Now, $g_i\cdot \zeta_1^i$ and $g_i\cdot\zeta_2^i$ map by $q_i$ to points in
  simplices adjacent to $x_1$ and $x_2$, so by Lemma~\ref{lem:propermaps} the
  sequences we can pass to a subsequence so that the sequences $g_i\cdot
  \zeta_1^i$ and $g_i\cdot\zeta_2^i$ converge to points $\zeta_1$ and $\zeta_2$
  in $\boundary G - \set\xi$ as $i \to \infty$.
  \todo{finish this}
\end{proof}

@@

\begin{proposition}
  Suppose that $G$ satisfies $\ddag'_M$ for $M = D+2$. Then there exists $k$
  such that for $n$ sufficiently large there is a map
  $i^n_{n+1}\from \Skel_1 K_n \to \Skel_1 K_{n+1}$ satisfying the following
  conditions:
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_k\Skel_1 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq ?$, and
    \item for each $n$, the map $i^n_{n+1}$ is affine homotopic to a map that
      factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
  \end{enumerate}
\end{proposition}

\begin{proof}
  \todo{Prove this}
\end{proof}

@@

\todo{Proposition below}

\begin{proposition}\label{prop:extendingaffinemaps2}
  Something about extending affine maps.
\end{proposition}

@@

We will make frequent use of the following lemma, adapted 
from~\cite{bestvinamess91}

>>>>

\begin{lemma}\label{lem:uniform_continuity}
  For any compact subset $C \subset \boundary G - \set\xi$ there exists $i_0$
  and $\epsilon > 0$ such that $C \in U_i$ for $i \geq i_0$, and so that
  $\newdist(q_i(\zeta_1), q_i(\zeta_2)) \leq ?$ whenever $i \geq i_0$ and
  $\zeta_1$ and $\zeta_2$ are points in $C$ with $\rho(\zeta_1, \zeta_2) \leq
  \epsilon$.
\end{lemma}

\begin{proof}
  \todo{Prove this uniform continuity statement.}
\end{proof}

@@

  Now, $g_i\cdot \zeta_1^i$ and $g_i\cdot\zeta_2^i$ map by $q_i$ to points in
  simplices adjacent to $x_1$ and $x_2$, so by Lemma~\ref{lem:propermaps} the
  sequences we can pass to a subsequence so that the sequences $g_i\cdot
  \zeta_1^i$ and $g_i\cdot\zeta_2^i$ converge to points $\zeta_1$ and $\zeta_2$
  in $\boundary G - \set\xi$ as $i \to \infty$.

  Let $C$ be a compact subset of $\boundary G - \set\xi$ containing a path
  $\beta$ from $\zeta_1$ to $\zeta_2$ and also a neighbourhood of each of the
  points $\zeta_1$ and $\zeta_2$. Let $\epsilon$ and $i_0$ be as in
  Lemma~\ref{lem:uniform_continuity}. By increasing $i_0$ we may also assume
  that $\zeta_1^i$ and $\zeta_2^i$ are contained in $C$ for $i \geq i_0$. By
  decreasing $\epsilon$ we may assume that the $\epsilon$-neighbourhoods of
  $\zeta_1$ and $\zeta_2$ are contained in $C$.

  Since $\boundary G$ is locally path connected, there exists a neighbourhood
  of $\zeta_1$ (repsectively $\zeta_2$) such that any point in this
  neighbourhood is joined to $\zeta_1$ (respectively $\zeta_2$) by a path
  contained in the $\epsilon$-neighbourhood of $\zeta_1$. Now increase $i_0$ to
  ensure that $\zeta_1^i$ and $\zeta_2^i$ are contained in these neighbourhoods
  for $i \geq i_0$. Let $\alpha_1^i$ (respectively $\alpha_2^i$) be a path in
  the ball of radius $\epsilon$ centred at $\zeta_1$ (respectively $\zeta_2$)
  connecting $\zeta_1^i$ (repsectively $\zeta_2^i$) to $\zeta_1$ (respectively
  $\zeta_2$.)

  Then the concatenation of $\alpha_1^i$, $\beta$ and $\alpha_2^i$ gives a path
  in $C$ from $\zeta_1^i$ to $\zeta_2^i$ that can be cut into boundedly many
  subpaths of diameter at most $\epsilon$. It follows that the composition of
  this path with $q_i$ is a path that admits a simplicial approximation
  connecting $x_1$ to $x_2$ after boundedly many subdivisions of the interval.
  For $i \geq i_0$ sufficiently large this gives a contradiction.
  \todo{Check this paragraph.}
\end{proof}

@@

In what follows we will make use of the following lemma, adapted from
from~\cite{bestvinamess91}

\begin{proposition}
  Suppose that $G$ satisfies $\ddag'_M$ for $M = ?$. Then there exists $k$
  such that for $n$ sufficiently large there is a map
  $i^n_{n+1}\from \Skel_1 K_n \to \Skel_1 K_{n+1}$ satisfying the following
  conditions:
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_k\Skel_1 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq ?$, and
    \item for each $n$, the map $i^n_{n+1}$ is affine homotopic to a map that
      factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
  \end{enumerate}
\end{proposition}

\begin{proof}
  First we define $i^n_{n+1}$ on the vertex set of $K_n$. For a vertex $x$ of
  $K_n$, let $\alpha$ be a geodesic with $\dist(x, \alpha(n)) \leq 4\delta$ and
  let $i^n_{n+1}(x)$ be any vertex of the minimal simplex of $K_{n+1}$
  containing $p^\infty_{n+1}(\gamma_x(\infty))$. Then the second claimed
  property follows from \todo{why?}

  For an edge $e$ of $K_n$, the distance between the images of the end points
  of $e$ under $i^n_{n+1}$ is at most \todo{?} and it follows that \todo{prove
  this}.
\end{proof}

@@

\begin{proposition}\label{prop:extendingaffinemaps2}
  \todo{Proposition about extending affine maps.}
\end{proposition}

@@
